The Astropy Project: xx

### 2021-12-01 src/ms.tex
more intro words

One of the factors that has led to its rapid ascent in popularity in scientific
contexts has been significant volunteer-driven effort behind developing
community-oriented open-source software tools and fostering communities of users
and developers that have grown around these packages.
TODO: Numpy, scipy, matplotlib, scientific software ecosystem.
The astropy core package ... one of the first large, community-oriented, open-source \python packages ... was Astropy ... (note: yt)
TODO: words about astropy core package.
TODO: The core package is now largely stable and provides core foundational tools.

TODO: Astropy has expanded to become the Astropy Project: Broader scope than core package. Core package, Ecosystem of tools, Community of users, developers, maintainers

TODO:  https://physicsworld.com/a/standing-on-the-shoulders-of-programmers/

>>>>

One of the factors that has led to its rapid ascent in popularity in scientific
contexts has been the significant, volunteer-driven effort behind developing
community-oriented open-source software tools and fostering communities of users
and developers that have grown around these efforts.
Today, a broad and feature-diverse ``ecosystem'' of packages exists in the
\python scientific computing landscape: Roughly ordered from general-use to
domain-specific, this landscape now includes packages that provide core
numerical analysis functionality like \package{numpy} \citep{todo} and
\package{scipy} \citep{todo}, to visualization frameworks like
\package{matplotlib} \citep{todo}, to machine learning and data analysis
packages like \package{tensorflow} \citep{todo}, \package{pymc3} \citep{todo},
and \package{emcee} \citep{todo}, to specialized, domain-specific packages like
\package{yt} \citep{todo}, \package{plasmapy} \citep{todo}, \package{sunpy}
\citep{todo}, \package{Biopython} \citep{todo}, and \package{sympy}
\citep{sympy} (to name a few in each category).
The \astropypkg \citep{astropy:2013, astropy:2018} core package began as an
effort to consolidate the development of commonly-used functionality needed to
perform astronomical research into a community-developed \python package.

The \astropypkg core package was one of the first large, open-source \python
packages developed for astronomy and provides, among other things, software
functionality for reading and writing astronomy-specific data formats (e.g.,
FITS), transforming and representing astronomical coordinates, and representing
and propagating physical units in code.
An early description of the core functionality in \astropypkg can be found in
the first Astropy paper \citep{astropy:2013} or in detail in the core package
documentation.\footnote{\url{https://docs.astropy.org/}}
The \astropypkg core package is now largely stable in that the software
interface does not change without sufficient and significant motivation, and the
addition of new features into the core package has slowed significantly as
compared to the first years of its development.
This is largely driven by the fact that the name Astropy has grown in scope to
become ``the Astropy Project'': A name used to refer to the union of the
\astropypkg core package, the ecosystem of astronomy-specific software tools
that are interoperable with \astropypkg, \emph{and} the community of users,
developers, and maintainers that participate in Astropy efforts.

% TODO:  https://physicsworld.com/a/standing-on-the-shoulders-of-programmers/
